---
title: "EDS-212-Day5_Probabilities"
author: "Oksana Protsukha"
format: 
  html: 
    code-fold: true
    code-summary: "View code"
editor: visual
execute:
  echo: true
  warning: false
---

```{r}
library(tidyverse)
```

## Explore starwars dataset

```{r}
head(starwars)
```

```{r}
dim(starwars)
```

```{r}
ggplot(data = starwars, aes(x = height)) +
  geom_histogram()
```

```{r}
# --- dependendent variable should be on the y axis (e.g. y depends on x - mass depends on height)
ggplot(data = starwars, aes(x = height, y = mass, color = sex)) +
  geom_point()
```

## Summary statistics

```{r}
# --- view all vectors for a given coloumn: dataset$coloumn
starwars$height
```

-   Use mean() function to find means

-   Use sd() functions to find standard deviations

#### Find and store the mean of character heights

```{r}
# --- if there a fields with missing values, by default R returns NA to indicate that it was not able to calculate mean for the given dataset

mean_height <- mean(starwars$height)
mean_height

# --- exclude NA values from the dataset to calculate mean
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_height
```

#### Find and store the standard deviation of character heights

```{r}
# --- if there a fields with missing values, by default R returns NA to indicate that it was not able to calculate standard deviation for the given dataset

sd_height <- sd(starwars$height)
sd_height

# --- exclude NA values from the dataset to calculate standard deviation
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
```

## In-line reporting using code outputs

The mean height of star wars characters is `r mean_height` cm with a standard deviation of `r sd_height`
